---
title: "final plots - ee revisions"
author: "Sam Ozminkowski"
date: "2023-10-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(cowplot)
library(emojifont)
library(grid)
library(gridExtra)
```


# Final plots - Realistic Simulations

- We will base the plots on the existing functions in [plot_result.R](https://github.com/samozm/bayesian_network_regression_imp/blob/main/additional_materials/plot_results.R).
- The result files are in the [Google Drive](https://drive.google.com/drive/u/2/folders/1obkVu6qJfC6tdNAnLFHhsSSn9SUwTxE2) which we downloaded and put in the github repo (but gitignored).

```{r}
setwd("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/additional_materials")
source("plot_results.R")
```

Three types of plots:

### 1. Grid plot (x=effect size, y=sparsity) for posterior probability of influential nodes

Function to create the plot:
```{r}
plot.nodes = function(pi,mu,path,simnum,R,nu,k,n,simtype=NULL,edgemu=NULL,yaxis=TRUE){
## Reading csv output files and appending
nodes <- data.frame()
nonc <- rep(F,4)
i <- 1 

for(i.pi in pi)
{
  for(j.mu in mu)
  {
    flnm2 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"psrf",n,simtype,edgemu)
    psrf <- read.csv(flnm2)[1,]
    if ((psrf$max_gamma[1] > 1.01 || psrf$max_xi[1] > 1.01))
    {
      nonc[i] <- T
    }
    flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"nodes",n,simtype,edgemu)
    nodes <- rbind(nodes, read.csv(flnm))
    i <- i + 1
  }
}

if(nrow(nodes) == 0)
{
  return(0)
}

## Labelling the nodes:
nn <- length(nodes$TrueXi) / (length(pi)*length(mu))
nodes$microbe <- rep(1:nn,length(pi)*length(mu))

if(yaxis){
  ylabel = "PP inftl. node"
  axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
}else{
  ylabel = ""
  axisTextY = element_blank()
}

## Plot:
plt <- ggplot(data=nodes,aes(x=microbe,y=Xi.posterior,fill=TrueXi)) + 
    geom_bar(stat="Identity") + xlab("") + ylab(ylabel) + 
    ggtitle(paste0("k=",k,", n=",n))+
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(1.2)),
        axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = axisTextY,
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2))
        ) +
    ##scale_fill_manual(values=c("#FF0000","#0000FF")) + 
    ##scale_fill_manual(values=c("#FF1493","#0000CD")) + 
  scale_fill_manual(values=c("#82AFBC","#0E4B87")) + 
    guides(fill="none") +
    scale_y_continuous(position="right",breaks = c(0,0.5,1),limits=c(0,1.05)) + 
    facet_grid(pi ~ mu, 
               switch="both",
              labeller = labeller(
                mu = c(`0.8` = "\u03BC=0.8", `1.2` = "\u03BC=1.2", `1.4` = "\u03BC=1.4", `1.6` = "\u03BC=1.6"),
                pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.5` = "\u03C0=0.5", `0.7` = "\u03C0=0.7", `0.8` = "\u03C0=0.8")
              ),
              as.table = FALSE)
  
#if (nonc[1])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(0.8,levels = c('0.8','1.6')),
#                       pi = factor(0.3,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[2])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(1.6,levels = c('0.8','1.6')),
#                       pi = factor(0.3,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[3])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(0.8,levels = c('0.8','1.6')),
#                       pi = factor(0.8,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[4])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(1.6,levels = c('0.8','1.6')),
#                       pi = factor(0.8,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}


return(plt)
}
```

### 2. Credible intervals for edge effects

Plotting function:
```{r}
## lim=limits for Y axis
plot.intervals <- function(simnum,pi,mu,R,nu,k,path,n,lim,simtype=NULL,edgemu=NULL)
{
  nonc <- F
  flnm2 <- make.filename(path,simnum,pi,mu,R,nu,k,"psrf",n,simtype,edgemu)
  if(!file.exists(flnm2)) { print(paste0(flnm2, " does not exist")); return() }
  psrf <- read.csv(flnm2)[1,]
  if ((psrf$max_gamma[1] > 1.01 || psrf$max_xi[1] > 1.01))
  {
    nonc <- T
  }
  flnm <- make.filename(path,simnum,pi,mu,R,nu,k,"edges",n,simtype,edgemu)
  edges <- read.csv(flnm)
  
  nn <- length(edges$true_B)
  edges$edge <- 1:nn
  edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,TRUE,FALSE))
  edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,TRUE,FALSE))
  
  if(pi>0.5){
    label = "True influential edges"
  }else{
    label = "True \n inf."
  }
  
  #lim_low <- floor(min(edges$X0.025)) - 0.25
  #lim_high <- ceiling(max(edges$X0.975)) + 0.25
  lim_low <- floor(quantile(edges$X0.025,0.025)-0.5)
  lim_high <- ceiling(quantile(edges$X0.975,0.975)+0.5)
  
  lim <- c(lim_low,lim_high)
    
  plt <- edges %>% ggplot() + geom_errorbar(aes(x=factor(edge),ymin=X0.025,
                                                                 ymax=X0.975,
                                                                 color=rej)) +
        xlab("") + ylab("")+ ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu))+
        scale_color_manual(values=c("#82AFBC","#0E4B87")) + 
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.2)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
          axis.ticks.y = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.position = "none"
        ) +
          #scale_x_continuous(limits=c(1,n)) + coord_flip() +
          #scale_y_continuous(limits=lim) +
          coord_flip(ylim=lim) + scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          geom_point(aes(x=factor(edge),y=mean, color=rej),shape=18, size=2) +
          geom_hline(aes(yintercept=0),linetype="solid",color="#696969", size=1) +
          ##geom_hline(aes(yintercept=mu),linetype="dashed",color="blue") +
          facet_grid(nonzero_mean ~.,scales="free_y",space="free_y", labeller = labeller(
            nonzero_mean = c(`TRUE` = label, `FALSE` = "True non-influential edges")
          )) 
  #if(nonc)
  #{
  #  plt <- plt + ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu, " - NOT CONV"))
  #}
  return(plt)
}
```

### 3. False positive/negative rates

```{r}
library(tidyr)
plot.false.pos.neg <- function(simnum,pi,mu,R,nu,k,path,n,simtype=NULL,edgemu=NULL, xaxis=FALSE, title=TRUE)
{
  
  nn <- length(k) * length(pi) * length(mu)
  fr.e <- data.frame(k=k,fpr_gamma=rep(0,nn), fpr_nodepp=rep(0,nn),
                      fnr_gamma=rep(0,nn), fnr_nodepp=rep(0,nn),
                      pi=rep(0,nn),mu=rep(0,nn))
  l <- 1
  
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      for(k.n in k)
      {
        
        flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"edges",n,
                              simtype,edgemu)
        edges <- read.csv(flnm)
        
        o <- length(edges$true_B)
        edges$edge <- 1:o
        edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,1,0))
        edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,1,0))
        edges <- transform(edges,zero_mean=ifelse(true_B == 0.0,1,0))
        edges <- transform(edges,fp=ifelse(rej==1 & nonzero_mean==0,1,0))
        edges <- transform(edges,fn=ifelse(rej==0 & nonzero_mean==1,1,0))
        
        flnm2 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"nodes",n,
                               simtype,edgemu)
        nodes <- read.csv(flnm2)
        
        m <- length(nodes$TrueXi)
        nodes$node <- 1:m
        nodes <- transform(nodes, rej=ifelse(Xi.posterior>=0.5,1,0))
        nodes <- transform(nodes, TrueXi=ifelse(TrueXi=='true',TRUE,FALSE))
        nodes <- transform(nodes,fp=ifelse(rej==1 & TrueXi==FALSE,1,0))
        nodes <- transform(nodes,fn=ifelse(rej==0 & TrueXi==TRUE,1,0))
        
        fr.e$fpr_nodepp[l] <- sum(nodes$fp) / sum(1 - nodes$TrueXi)
        fr.e$fnr_nodepp[l] <- sum(nodes$fn) / sum(nodes$TrueXi)

        fp.mat <- matrix(0,m,m)
        fp.mat[lower.tri(fp.mat, diag=T)] <- edges$fp
        fp.mat <- t(fp.mat)
        
        fn.mat <- matrix(0,m,m)
        fn.mat[lower.tri(fp.mat, diag=T)] <- edges$fn
        fn.mat <- t(fp.mat)
        
        nz.mat <- matrix(0,m,m)
        nz.mat[lower.tri(nz.mat, diag=T)] <- edges$nonzero_mean
        nz.mat <- t(nz.mat)
        
        
        fr.e$fpr_gamma[l] <- sum(diag(fp.mat)) / sum(1 - diag(nz.mat))
        fr.e$fnr_gamma[l] <- sum(diag(fn.mat)) / sum(diag(nz.mat))
        fr.e$pi[l] <- i.pi
        fr.e$mu[l] <- j.mu
        fr.e$n_microbes[l] <- k.n
        
        
        l <- l+1
      }
    }
  }
  
  ## Manipulate df
  df = gather(fr.e,"type","value",2:5)
  df = within(df, type <- factor(type))
  
  ## added something so that bars appear even with 0.0
  df$value[df$value == 0.0] = 0.005
  
  if(xaxis){
  xlabel = "Number of sampled nodes"
  }else{
  xlabel = ""
  }
  
  plt <- ggplot(data=df,aes(x=k,y=value,fill=type)) + 
    geom_bar(position="dodge", stat="identity") +
    ylab("")+xlab(xlabel)+
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(1.8)),
        axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"), 
        axis.text.y = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"),
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2)),
        legend.title = element_blank(),
        legend.text = element_text(size = rel(1.5))
        ) +
    scale_fill_manual(values=c("#82AFBC", "#9999CC", "#0E4B87", "#4C0099")) + 
    scale_x_continuous(breaks=k) +
    #guides(fill="none") +
    scale_y_continuous(position="right",breaks = c(0,0.5,1),limits=c(0,1)) + 
    facet_grid(pi ~ mu, 
               switch="y",
              labeller = labeller(
                mu = c(`0.8` = "\u03BC=0.8", `1.2` = "\u03BC=1.2", `1.4` = "\u03BC=1.4", `1.6` = "\u03BC=1.6"),
                pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.5` = "\u03C0=0.5", `0.7` = "\u03C0=0.7", `0.8` = "\u03C0=0.8")
              ),
              as.table = FALSE) # paste0("\u03C0=",pi,", \u03BC=",mu)
  
  if(title && !is.null(simtype)){
    tl_ar <- strsplit(simtype,"_")[[1]]
     #print(tl_ar)
    if(tl_ar[2] == "phylo"){
      tl_ar[2] = "phylogenetic"
    }
    if(tl_ar[1] == "additive"){
      tl_ar[1] = "Additive"
    }
    else if(tl_ar[1] == "interaction")
    {
       tl_ar[1] = "Interaction"
    }
    else
    {
       tl_ar[1] = "Functional redundancy"
    }
    print(tl_ar)
    plt <- plt + ggtitle(paste0(tl_ar,collapse=" ")) + theme(legend.position = "top")
    plt <- plt + ggtitle(paste0("n = ",n)) + theme(legend.position = "top")
  }else{
      plt <- plt + theme(legend.position = "none") 
  }
  
  return(plt)
}
```

### 4. MSE plot: x=number of microbes, y=MSE, lines/colors for sparsity/effect size

Plotting function:
```{r}
library(tidyr)
plot.MSE <- function(simnum,pi,mu,R,nu,k,path,n, simtype=NULL,edgemu=NULL,leg=TRUE,maxlim=0,ylab=TRUE)
{
  mse <- data.frame()
  betas <- data.frame()
  a <- 1
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      for(k.n in k)
      {
        flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"MSE",n,
                              simtype,edgemu)
        if(!file.exists(flnm)) { print(paste0(flnm, " does not exist")); return() }
        mse <- rbind(mse,read.csv(flnm))
        
        flnm2 <- paste0("/Users/samoz/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/data/simulation/realistic/edge_mu=0.4_mu=",
                        j.mu,"_n_microbes=",k.n,"_out=bs_pi=",i.pi,"_samplesize=",n,"_simnum=2_type=",simtype,".csv")
        betas <- read.csv(flnm2)
        bta.mat <- matrix(0,30,30)
        bta.mat[lower.tri(bta.mat, diag=T)] <- betas$B
        diag(bta.mat) <- 0
        bta.mat <- t(bta.mat)
        
        flnm3 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"edges",n,
                               simtype,edgemu)
        edges <- read.csv(flnm3)
        edg.mat <- matrix(0,30,30)
        edg.mat[lower.tri(edg.mat, diag=T)] <- edges$mean
        diag(edg.mat) <- 0
        edg.mat <- t(edg.mat)
        
        V <- 30
        mse$MSE[a] <- sum((bta.mat - edg.mat)^2)*2/(V*(V-1))
        a <- a + 1
      }
    }
  }
  
  if(maxlim == 0)
  {    
    maxlim <- 1
  }
  
  y_label = ""
  
  if(ylab)
  {
    y_label = "MSE"
  }
  
  ## Manipulate mse df
  df = gather(mse,"type","value",1:2)
  df = within(df, type <- factor(type, labels=c("Coef.", "Response")))
  
  plt <- ggplot(df, aes(x=n_microbes, y=value, group=interaction(pi,mu),color=factor(pi), 
                  linetype=factor(mu)))  + 
    geom_line(size=1.7) + labs(x="# microbes sampled", y = y_label,
                               color="\u03C0", # pi
                               linetype="\u03BC" # mu
                               ) +
    ggtitle(paste0("n = ",n))+
    theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.9)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          axis.text = element_text(colour="grey", size=rel(1.2), hjust=.5, vjust=.5, face="plain"),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.text=element_text(size=rel(1.2)),
          legend.title=element_text(size=rel(1.2))
        ) +
    ##scale_color_manual(values=c("#3CB371","#FF8C00")) + 
    scale_color_manual(values=c("#E59CBD","#C41044")) + 
    scale_x_continuous(breaks=mse$n_microbes) + 
    scale_y_continuous(
                       breaks=seq(0,maxlim,maxlim/4))+
        facet_grid(. ~ type, 
              as.table = FALSE)
  if(maxlim > 0)
  {
    plt <- plt + coord_cartesian(ylim=c(0,maxlim))
  }
  if(!leg){
    plt <- plt + theme(legend.position = "none")
  }
  return(plt)
}
```

### 5. Plot credible intervals for nodes
```{r}
plot.ci.nodes <- function(simnum,pi,mu,R,nu,k,path,n,lim,simtype=NULL,edgemu=NULL, ylab=T,xticks=T)
{
  nodes <- data.frame()
  nonc <- F

  flnm2 <- make.filename(path,simnum,pi,mu,R,nu,k,"psrf",n,simtype,edgemu)
  if(!file.exists(flnm2)) { print(paste0(flnm2, " does not exist")); return() }
  psrf <- read.csv(flnm2)[1,]
  if ((psrf$max_gamma[1] > 1.01 || psrf$max_xi[1] > 1.01))
  {
    nonc <- T
  }
  flnm <- make.filename(path,simnum,pi,mu,R,nu,k,"edges",n,simtype,edgemu)
  edges <- read.csv(flnm)
  
  nn <- length(edges$true_B)
  edges$edge <- 1:nn
  edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,TRUE,FALSE))
  edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,TRUE,FALSE))
  
  label = "True inf."
  
  flnm3 <- make.filename(path,simnum,pi,mu,R,nu,k,"nodes",n,simtype,edgemu)
  nodes <- read.csv(flnm3)
  
  ## Labelling the nodes:
  nn <- length(nodes$TrueXi) / (length(pi)*length(mu))
  nodes$microbe <- rep(1:nn,length(pi)*length(mu))
  
  n.len <- length(nodes$TrueXi)
  
  mat <- matrix(0,n.len,n.len)
  mat[lower.tri(mat, diag=T)] <- edges$mean
  mat <- t(mat)
  
  lower.mat <- matrix(0,n.len,n.len)
  lower.mat[lower.tri(lower.mat, diag=T)] <- edges$X0.025
  lower.mat <- t(lower.mat)
  
  upper.mat <- matrix(0,n.len,n.len)
  upper.mat[lower.tri(upper.mat, diag=T)] <- edges$X0.975
  upper.mat <- t(upper.mat)
  
  nonzero.mat <- matrix(0,n.len,n.len)
  nonzero.mat[lower.tri(nonzero.mat, diag=T)] <- edges$nonzero_mean
  nonzero.mat <- t(nonzero.mat)
  
  rej.mat <- matrix(0,n.len,n.len)
  rej.mat[lower.tri(rej.mat, diag=T)] <- edges$rej
  rej.mat <- t(rej.mat)
  
  #print("main effect coefficients")
  coefdf <- data.frame(lower=diag(lower.mat),coef=diag(mat),
                       upper=diag(upper.mat),nodepp=nodes$Xi.posterior,
                       true_inf=nodes$TrueXi,
                       node=1:length(diag(lower.mat)),
                       nonzero_mean=as.factor(diag(nonzero.mat)),
                       rej = as.factor(diag(rej.mat))
                       )
  
  lim_low <- floor(min(coefdf$lower)) - 0.25
  lim_high <- ceiling(max(coefdf$upper)) + 0.25
  lim <- c(lim_low,lim_high)
  
  if(ylab){
    ylabel2 = "PP"
    axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
  }else{
    ylabel2 = ""
    axisTextY = element_blank()
  }
  if(ylab){
    ylabel = expression(beta)
    axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
  }else{
    ylabel = ""
    axisTextY = element_blank()
  }
  if(xticks){
    xlabel = "Microbe"
    axisLabsX = element_text()
  }
  else
  {
    xlabel = ""
    axisLabsX = element_blank()
  }
  
  plt1 <- coefdf %>% ggplot() + geom_errorbar(aes(x=factor(node),ymin=lower,
                                                                 ymax=upper,
                                                                 color=rej)) +
        xlab("") + ylab(ylabel)+ #ggtitle(paste0("\u03C0=",pi," \u03BC=",mu))+
        scale_color_manual(values=c("#82AFBC","#0E4B87")) + 
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(2)),
          axis.title.y = element_text(size=rel(2), angle=90, vjust=0.5, hjust=0.5),
          #axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
          axis.text.x=element_blank(), 
          axis.ticks.x=element_blank(),
          axis.ticks.y = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.position = "none",
          plot.margin = margin(b=-0.25, unit="cm")
        ) +
          #scale_x_continuous(limits=c(1,n)) + coord_flip() +
          #scale_y_continuous(limits=lim) +
          #coord_flip() + scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          #scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          geom_point(aes(x=factor(node),y=coef, color=rej),shape=18, size=2) +
          geom_hline(aes(yintercept=0),linetype="solid",color="#696969", size=1) +
          ##geom_hline(aes(yintercept=mu),linetype="dashed",color="blue") +
          facet_grid(.~nonzero_mean,scales="free_x",space="free_x", 
                     labeller = labeller(
                                  nonzero_mean = c(`0` = "non-inf.",
                                                   `1` = "true inf.")
          ))
  
  view_lim <- c(max(lim_low,-10),min(lim_high,10))
  
  plt1 <- plt1 + coord_cartesian(ylim = view_lim)
  
  plt2 <- ggplot(data=coefdf,aes(x=factor(node),y=nodepp,fill=rej)) + 
    geom_bar(stat="Identity") + xlab(xlabel) + ylab(ylabel2) + 
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(2)),
        axis.title.y = element_text(size=rel(2), angle=90, vjust=0.5, hjust=0.5),
        #axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        #axis.text.y = axisTextY,
        #axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
        axis.text.x = axisLabsX,
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2)),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        plot.margin = margin(t=-0.25, unit="cm")
        ) +
  scale_fill_manual(values=c("#82AFBC","#0E4B87")) + 
    guides(fill="none") +
    scale_y_continuous(breaks = c(0,0.5,1),limits=c(0,1.05)) + 
    facet_grid(.~nonzero_mean,scales="free_x",space="free_x", 
                     labeller = labeller(
                                  nonzero_mean = c(`1` = "", 
                                                   `0` = "")
          ))
  
  #if(nonc)
  #{
  #  plt1 <- plt1 + ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu, " - NOT CONV."))
  #  plt2 <- plt2 + ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu, " - NOT CONV."))
  #}

  return(list(plt1,plt2))
}
```

Fixed parameters for all plots:
```{r}
path = "~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/simulation/current-wid/realistic-results/"
mu = c(0.8,1.6)
pi = c(0.3,0.8)
nu=10
simnum = 2
edgemu = 0.4
R=7
```

For all the realistic simulation plots, we use the same functions defined for the unrealistic simulations.

```{r}
simtypes = c("additive_random","additive_phylo",
             "redundant_random","redundant_phylo",
             "interaction_random","interaction_phylo")
ns = c(500,1000)
ks = c(8,22)
```


```{r}
for(simtype in simtypes)
{
  for(n in ns)
  {
    #(simnum,pi,mu,R,nu,k,path,n, simtype=NULL,edgemu=NULL,leg=TRUE)
    for(k in ks)
    {
      #plt = plot.nodes(pi,mu,path,simnum,R,nu,k,n, simtype=simtype, edgemu=edgemu)
      #plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/nodes/plot-nodes-n",n,"-k",k,"-R",R,"-",simtype,".pdf")
      
      #pdf(plotname,height=6, width=7)
      #print(plt)
      #dev.off()
      
      plts = list(rep(0,4))
      l <- 1
      for(i.pi in pi)
      {
        for(j.mu in mu)
        {
          plt = plot.intervals(simnum,i.pi,j.mu,R,nu,k,path,n,c(-4,4), simtype=simtype,edgemu=edgemu)
          plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/intervals/plot-intervals-n",n,"-k",k,"-R",R,"-pi",i.pi,"-mu",j.mu,"-",simtype,".pdf")
          
          pdf(plotname,height=14, width=4)
          print(plt)
          dev.off()
          
          plt = plot.ci.nodes(simnum,i.pi,j.mu,R,nu,k,path,n,c(-4,4), ylab=(i.pi==0.3), xticks=(j.mu==0.8), simtype=simtype,edgemu=edgemu)
          pilab <- FALSE
          mulab <- FALSE
          
         pilab <- (j.mu == 1.6)
          mulab <- (i.pi == 0.8)
          
          pg1 <- plot_grid(plt[[1]], plt[[2]], ncol=1, align="v", rel_heights = c(1.2,1))
          if(pilab && mulab)
          {  
            pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
            mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
            plts[[l]] <- plot_grid(pilab,plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08)),ncol=1,rel_heights = c(0.08,1))
          }
          else if(pilab)
          {
            pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
            plts[[l]] <- plot_grid(pilab,pg1,ncol=1,rel_heights = c(0.08,1))
          }
          else if(mulab)
          {
            mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
            plts[[l]] <- plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08))
          }
          else{
            plts[[l]] <- pg1
          }
          l <- l + 1
        }
      }
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/nodes/plot-ci-nodes-n",n,"-k",k,"-R",R,"-",simtype,".pdf")
          
      pdf(plotname,height=10, width=12)
      
      split_type <- strsplit(simtype,"_")
      #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]), ", n=",n," k=", k), fontface='bold')
      
      print( plot_grid(plts[[2]], plts[[4]], plts[[1]], plts[[3]], ncol=2,align="v") )
      dev.off()
    }
  }
}

```

```{r}
ns <- c(500,1000)
R <- 7
nu <- 10
for(simtype in simtypes)
{
  maxlim <- 10
  if(simtype %in% c("interaction_random","interaction_phylo"))
  {
    maxlim <- 5
  }
  else if(simtype %in% c("additive_random","additive_phylo"))
  {
    maxlim <- 1
  }
  else
  {
    maxlim <- 2.5
  }
  MSE.plots <- list(rep(0,length(ns)))
  a <- 1
  for(n in ns)
  {
    MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,ks,path,n,simtype=simtype,leg=(n==1000),edgemu=edgemu,maxlim=maxlim,ylab=(n==500))
    a <- a + 1
  }
  
  if(length(MSE.plots) == 0 ){next}
  plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/MSE/plot-MSE-n-500-1000-R",R,"-",simtype,".pdf")
  pdf(plotname,height=6, width=10)

  split_type <- strsplit(simtype,"_")
  #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]),", R=",R), fontface='bold')
    
  plt1 <- plot_grid(MSE.plots[[1]],MSE.plots[[2]],nrow=1,align='h',rel_widths = c(1,1.2))
  print(plt1)
  dev.off()
}
```

```{r}
ns <- c(50,100)
Rs <- c(5)
nus <- c(10,12,16)
for(simtype in simtypes)
{
  for(R in Rs)
  {
    for(nu in nus)
    {  
      mse <- data.frame()
      
      if(simtype %in% c("interaction_random","interaction_phylo"))
      {
        maxlim <- 5
      }
      else if(simtype %in% c("additive_random","additive_phylo"))
      {
        maxlim <- 0.5
      }
      else
      {
        maxlim <- 1
      }
      maxlim <- 0
      MSE.plots <- list(rep(0,length(ns)))
      a <- 1
      for(n in ns)
      {
        MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,ks,path,n,simtype=simtype,leg=(n==100),edgemu=edgemu,maxlim=maxlim,ylab=(n==50))
        a <- a + 1
        flnm <- make.filename(path,2,0.3,0.8,R,nu,8,"psrf",n,simtype=simtype,edge_mu=0.4)
        if(!file.exists(flnm)) { print(paste0(flnm, " does not exist")); next }
        
        for(k in ks)
        {
          plts = list(rep(0,4))
          l <- 1
          for(i.pi in pi)
          {
            for(j.mu in mu)
            {
              plt = plot.ci.nodes(simnum,i.pi,j.mu,R,nu,k,path,n,c(-4,4), ylab=(i.pi==0.3), xticks=(j.mu==0.8), simtype=simtype,edgemu=edgemu)
              pilab <- FALSE
              mulab <- FALSE
              
              pilab <- (j.mu == 1.6)
              mulab <- (i.pi == 0.8)
              
              pg1 <- plot_grid(plt[[1]], plt[[2]], ncol=1, align="v", rel_heights = c(1.2,1))
              if(pilab && mulab)
              {  
                pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
                mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
                plts[[l]] <- plot_grid(pilab,plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08)),ncol=1,rel_heights = c(0.08,1))
              }
              else if(pilab)
              {
                pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
                plts[[l]] <- plot_grid(pilab,pg1,ncol=1,rel_heights = c(0.08,1))
              }
              else if(mulab)
              {
                mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
                plts[[l]] <- plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08))
              }
              else{
                plts[[l]] <- pg1
              }
              l <- l + 1
            }
          }
          plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/nodes/plot-ci-nodes-n",n,"-k",k,"-R",R,"-nu",nu,"-",simtype,".pdf")
              
          pdf(plotname,height=10, width=12)
          
          split_type <- strsplit(simtype,"_")
          #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]), ", n=",n," k=", k), fontface='bold')
          
          print(plot_grid(plts[[2]], plts[[4]], plts[[1]], plts[[3]], ncol=2,align="v"))
          dev.off()
        }
      }
      
      if(length(MSE.plots) <= 1 ){next}
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/MSE/plot-MSE-n-50-100-R",R,"-nu",nu,"-",simtype,".pdf")
      pdf(plotname,height=6, width=10)

      split_type <- strsplit(simtype,"_")
      #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]),", R=",R," nu=",nu), fontface='bold')
        
      plt1 <- plot_grid(MSE.plots[[1]],MSE.plots[[2]],nrow=1,align='h',rel_widths = c(1,1.2))
      print(plt1)
      #print(plot_grid(title,plt1,ncol=1,align='v',rel_heights = c(0.05,1)))
      dev.off()
    }
  }
}
```


```{r}
ns <- c(50,200)
Rs <- c(5)
nus <- c(10,12,16)
for(simtype in simtypes)
{
  for(R in Rs)
  {
    for(nu in nus)
    {  
      mse <- data.frame()
      
      if(simtype %in% c("interaction_random","interaction_phylo"))
      {
        maxlim <- 5
      }
      else if(simtype %in% c("additive_random","additive_phylo"))
      {
        maxlim <- 0.5
      }
      else if(simtype == "redundant_phylo")
      {
        maxlim <- 6
      }
      else
      {
        maxlim <- 5
      }
      MSE.plots <- list(rep(0,length(ns)))
      a <- 1
      for(n in ns)
      {
        MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,ks,path,n,simtype=simtype,leg=(n==200),edgemu=edgemu,maxlim=maxlim,ylab=(n==50))
        a <- a + 1
        flnm <- make.filename(path,2,0.3,0.8,R,nu,8,"psrf",n,simtype=simtype,edge_mu=0.4)
        if(!file.exists(flnm)) { print(paste0(flnm, " does not exist")); next }
        
        for(k in ks)
        {
          plts = list(rep(0,4))
          l <- 1
          for(i.pi in pi)
          {
            for(j.mu in mu)
            {
              plt = plot.ci.nodes(simnum,i.pi,j.mu,R,nu,k,path,n,c(-4,4), ylab=(i.pi==0.3), xticks=(j.mu==0.8), simtype=simtype,edgemu=edgemu)
              pilab <- FALSE
              mulab <- FALSE
              
              pilab <- (j.mu == 1.6)
              mulab <- (i.pi == 0.8)
              
              pg1 <- plot_grid(plt[[1]], plt[[2]], ncol=1, align="v", rel_heights = c(1.2,1))
              if(pilab && mulab)
              {  
                pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
                mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
                plts[[l]] <- plot_grid(pilab,plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08)),ncol=1,rel_heights = c(0.08,1))
              }
              else if(pilab)
              {
                pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
                plts[[l]] <- plot_grid(pilab,pg1,ncol=1,rel_heights = c(0.08,1))
              }
              else if(mulab)
              {
                mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
                plts[[l]] <- plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08))
              }
              else{
                plts[[l]] <- pg1
              }
              l <- l + 1
            }
          }
          plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/nodes/plot-ci-nodes-n",n,"-k",k,"-R",R,"-nu",nu,"-",simtype,".pdf")
              
          pdf(plotname,height=10, width=12)
          
          split_type <- strsplit(simtype,"_")
          #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]), ", n=",n," k=", k), fontface='bold')
          
          print(plot_grid(plts[[2]], plts[[4]], plts[[1]], plts[[3]], ncol=2,align="v"))
          dev.off()
        }
      }
      
      if(length(MSE.plots) <= 1 ){next}
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/MSE/plot-MSE-n-50-200-R",R,"-nu",nu,"-",simtype,".pdf")
      pdf(plotname,height=6, width=10)
  
      split_type <- strsplit(simtype,"_")
      #title <- ggdraw() + draw_label(paste0(str_to_title(split_type[[1]][1]), " ", str_to_title(split_type[[1]][2]),", R=",R," nu=",nu), fontface='bold')
        
      plt1 <- plot_grid(MSE.plots[[1]],MSE.plots[[2]],nrow=1,align='h',rel_widths = c(1,1.2))
      print(plt1)
      #print(plot_grid(title,plt1,ncol=1,align='v',rel_heights = c(0.05,1)))
      dev.off()
    }
  }
}
```

### False PN

```{r}
all_k <- c(8,22)
R <- 7
nu <- 10
for(n in c(500,1000))
{
  for(simtype in c("redundant_random","redundant_phylo",
                   "interaction_random","interaction_phylo",
                   "additive_random","additive_phylo"))
  {
    plt = plot.false.pos.neg(simnum,pi,mu,R,nu,all_k,path,n,simtype=simtype,edgemu=edgemu, xaxis=TRUE, title=TRUE)
    plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/realistic/rates/plot-rates-n",n,"-R",R,"-",simtype,".pdf")
    
    pdf(plotname)
    print(plt)
    dev.off()
  }
  
}
```

