---
title: "final plots - ee revisions -- realistic"
author: "Sam Ozminkowski"
date: "2023-10-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(grid)
library(gridExtra)
library(cowplot)
library(emojifont)
```


# Final plots

- We will base the plots on the existing functions in [plot_result.R](https://github.com/samozm/bayesian_network_regression_imp/blob/main/additional_materials/plot_results.R).
- The result files are in the [Google Drive](https://drive.google.com/drive/u/2/folders/1obkVu6qJfC6tdNAnLFHhsSSn9SUwTxE2) which we downloaded and put in the github repo (but gitignored).

```{r}
setwd("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/additional_materials")
source("plot_results.R")
```


Five types of plots:

### 1. Grid plot (x=effect size, y=sparsity) for posterior probability of influential nodes

Function to create the plot:
```{r}
plot.nodes = function(pi,mu,path,simnum,R,nu,k,n,simtype=NULL,edgemu=NULL,yaxis=TRUE){
## Reading csv output files and appending
nodes <- data.frame()
nonc <- rep(F,4)
i <- 1 

for(i.pi in pi)
{
  for(j.mu in mu)
  {
    flnm2 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"psrf",n,simtype,edgemu)
    psrf <- read.csv(flnm2)[1,]
    if ((psrf$max_gamma[1] > 1.01 || psrf$max_xi[1] > 1.01))
    {
      nonc[i] <- T
    }
    flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"nodes",n,simtype,edgemu)
    nodes <- rbind(nodes, read.csv(flnm))
    i <- i + 1
  }
}

if(nrow(nodes) == 0)
{
  return(0)
}

## Labelling the nodes:
nn <- length(nodes$TrueXi) / (length(pi)*length(mu))
nodes$microbe <- rep(1:nn,length(pi)*length(mu))

if(yaxis){
  ylabel = "PP inftl. node"
  axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
}else{
  ylabel = ""
  axisTextY = element_blank()
}

## Plot:
plt <- ggplot(data=nodes,aes(x=microbe,y=Xi.posterior,fill=TrueXi)) + 
    geom_bar(stat="Identity") + xlab("") + ylab(ylabel) + 
    ggtitle(paste0("k=",k,", n=",n))+
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(1.2)),
        axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = axisTextY,
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2))
        ) +
    ##scale_fill_manual(values=c("#FF0000","#0000FF")) + 
    ##scale_fill_manual(values=c("#FF1493","#0000CD")) + 
  scale_fill_manual(values=c("#82AFBC","#0E4B87")) + 
    guides(fill="none") +
    scale_y_continuous(position="right",breaks = c(0,0.5,1),limits=c(0,1.05)) + 
    facet_grid(pi ~ mu, 
               switch="both",
              labeller = labeller(
                mu = c(`0.8` = "\u03BC=0.8", `1.2` = "\u03BC=1.2", `1.4` = "\u03BC=1.4", `1.6` = "\u03BC=1.6"),
                pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.5` = "\u03C0=0.5", `0.7` = "\u03C0=0.7", `0.8` = "\u03C0=0.8")
              ),
              as.table = FALSE)
  
#if (nonc[1])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(0.8,levels = c('0.8','1.6')),
#                       pi = factor(0.3,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[2])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(1.6,levels = c('0.8','1.6')),
#                       pi = factor(0.3,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[3])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(0.8,levels = c('0.8','1.6')),
#                       pi = factor(0.8,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}
#if (nonc[4])
#{
#  ann_text <- data.frame(microbe = 25,Xi.posterior = 1.025,lab = "Not Conv.",
#                       mu = factor(1.6,levels = c('0.8','1.6')),
#                       pi = factor(0.8,levels=c("0.3","0.8")), 
#                       TrueXi="false",
#                       R=R, n_microbes=k)
#  plt <- plt + geom_text(data = ann_text,label = "Not Conv.")
#}


return(plt)
}
```

### 2. Credible intervals for edge effects

Plotting function:
```{r}
## lim=limits for Y axis
plot.intervals <- function(simnum,pi,mu,R,nu,k,path,n,lim,simtype=NULL,edgemu=NULL)
{
  flnm <- make.filename(path,simnum,pi,mu,R,nu,k,"edges",n,simtype,edgemu)
  edges <- read.csv(flnm)
  
  nn <- length(edges$true_B)
  edges$edge <- 1:nn
  edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,TRUE,FALSE))
  edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,TRUE,FALSE))
  
  if(pi>0.5){
    label = "True influential edges"
  }else{
    label = "True \n inf."
  }
  
  lim_low <- floor(min(edges$X0.025)) - 0.25
  lim_high <- ceiling(max(edges$X0.975)) + 0.25
  lim <- c(lim_low,lim_high)
  
  plt <- edges %>% ggplot() + geom_errorbar(aes(x=factor(edge),ymin=X0.025,
                                                                 ymax=X0.975,
                                                                 color=rej)) +
        xlab("") + ylab("")+ ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu))+
        scale_color_manual(values=c("#82AFBC","#0E4B87")) +
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.2)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
          axis.ticks.y = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.position = "none"
        ) +
          #scale_x_continuous(limits=c(1,n)) + coord_flip() +
          scale_y_continuous(limits=lim) +
          coord_flip() + scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          geom_point(aes(x=factor(edge),y=mean, color=rej),shape=18, size=2) +
          geom_hline(aes(yintercept=0),linetype="solid",color="#696969", size=1) +
          ##geom_hline(aes(yintercept=mu),linetype="dashed",color="blue") +
          facet_grid(nonzero_mean ~.,scales="free_y",space="free_y", labeller = labeller(
            nonzero_mean = c(`TRUE` = label, `FALSE` = "True non-influential edges")
          )) 
  return(plt)
}
```

### 3. MSE plot: x=number of microbes, y=MSE, lines/colors for sparsity/effect size

Plotting function:
```{r}
library(tidyr)
plot.MSE <- function(simnum,pi,mu,R,nu,k,path,n, simtype=NULL,edgemu=NULL,leg=TRUE,ylab=TRUE)
{
  mse <- data.frame()
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      for(k.n in k)
      {
        flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"MSE",n,
                              simtype,edgemu)
        mse <- rbind(mse,read.csv(flnm))
      }
    }
  }
  
  y_label = ""
  
  if(ylab)
  {
    y_label = "MSE"
  }
  
  ## Manipulate mse df
  df = gather(mse,"type","value",1:2)
  df = within(df, type <- factor(type, labels=c("Coefficients", "Response")))
  
  plt <- ggplot(df, aes(x=n_microbes, y=value, group=interaction(pi,mu),color=factor(pi), 
                  linetype=factor(mu)))  + 
    geom_line(size=1.7) + labs(x="# microbes sampled", y = y_label, 
                               color="\u03C0", # pi
                               linetype="\u03BC" # mu
                               ) +
    ggtitle(paste0("n = ",n))+
    theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.9)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          axis.text = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.text=element_text(size=rel(1.2)),
          legend.title=element_text(size=rel(1.2))
        ) +
    ##scale_color_manual(values=c("#3CB371","#FF8C00")) + 
    scale_color_manual(values=c("#E59CBD","#C41044")) + 
    scale_x_continuous(breaks=mse$n_microbes) + 
    scale_y_continuous(limits=c(0,ceiling(max(mse$MSE))),
                       breaks=seq(0,ceiling(max(mse$MSE)),
                                  ceiling(max(mse$MSE))/10))+
        facet_grid(. ~ type, 
              as.table = FALSE)
  if(!leg){
    plt <- plt + theme(legend.position = "none")
  }
  return(plt)
}
```

### 4. Grid plot (x=effect size, y=sparsity) for MAP for B

Plotting function:
```{r}
plot.heatmap <- function(simnum,pi,mu,R,nu,k,path,n, simtype=NULL,edgemu=NULL)
{
  edges <- data.frame()
  
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"edges",n,simtype,edgemu)
      edge_df <- read.csv(flnm)
      V <- max(edge_df$x_microbe)
      edge_df$x_microbe <- rep(0,length(edge_df$x_microbe))
      edge_df$y_microbe <- rep(0,length(edge_df$y_microbe))
      l <- 1
      for(i in range(1,V))
      {
        for(j in range(i:V))
        {
          edge_df$x_microbe[l] <- i
          edge_df$y_microbe[l] <- j
          l <- l + 1
        }
      }
      edges <- rbind(edges, edge_df)
    }
  }
  
  nn <- length(edges$mean) / (length(pi)*length(mu))
  
  plt <- ggplot(edges, aes(x_microbe,y_microbe,fill=abs(mean))) + geom_tile() + 
    scale_y_reverse(breaks=1:(nn-1), labels=1:(nn-1), minor_breaks = seq(0.5,nn-0.5),
                    position="right") + 
    scale_x_continuous(breaks=2:nn, labels=2:nn, position="top", 
                       minor_breaks = seq(1.5,nn + 0.5)) +
    scale_fill_gradient(low="#FFFFFF", high="#4B0082",limits=c(0,8)) +
    labs(fill="MAP") + xlab("") + ylab("") +
    ggtitle(paste0("k=",k,", n=",n))+
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.9)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(2)),
          legend.text=element_text(size=rel(1.2)),
          legend.title=element_text(size=rel(1.2)),
          axis.text = element_blank(), axis.ticks = element_blank(),
        ) +
    facet_grid(pi ~ mu, switch="both",
               labeller = labeller(
                 mu = c(`0.8` = "\u03BC=0.8", `1.6` = "\u03BC=1.6"),
                 pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.8` = "\u03C0=0.8")
               ),
               as.table = FALSE) #paste0("\u03C0=",pi,", \u03BC=",mu)
  return(plt)
}

## true B values
plot.heatmap.true <- function(simnum,pi,mu,R,nu,k,path,n)
{
  edges <- data.frame()
  
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k,"edges",n,NULL,NULL)
      edges <- rbind(edges, read.csv(flnm))
    }
  }
  
  nn <- length(edges$mean) / (length(pi)*length(mu))
  
  plt <- ggplot(edges, aes(x_microbe,y_microbe,fill=abs(true_B))) + geom_tile() + 
    scale_y_reverse(breaks=1:(nn-1), labels=1:(nn-1), minor_breaks = seq(0.5,nn-0.5),
                    position="right") + 
    scale_x_continuous(breaks=2:nn, labels=2:nn, position="top", 
                       minor_breaks = seq(1.5,nn + 0.5)) +
    scale_fill_gradient(low="#FFFFFF", high="#191970",limits=c(0,8)) +
    labs(fill="True B") + xlab("") + ylab("") +
    ggtitle("True B matrix")+
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(1.9)),
          axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(2)),
          legend.text=element_text(size=rel(1.2)),
          legend.title=element_text(size=rel(1.2)),
          axis.text = element_blank(), axis.ticks = element_blank(),
        ) +
    facet_grid(pi ~ mu, switch="both",
               labeller = labeller(
                 mu = c(`0.8` = "\u03BC=0.8", `1.6` = "\u03BC=1.6"),
                 pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.8` = "\u03C0=0.8")
               ),
               as.table = FALSE)
  return(plt)
}
```

### 5. False positive/negative rates

```{r}
plot.false.pos.neg <- function(simnum,pi,mu,R,nu,k,path,n,simtype=NULL,edgemu=NULL, xaxis=FALSE, title=TRUE)
{
  
  nn <- length(k) * length(pi) * length(mu)
  fr.e <- data.frame(k=k,fpr_edges=rep(0,nn), fpr_nodes=rep(0,nn),
                      fnr_edges=rep(0,nn), fnr_nodes=rep(0,nn),
                      pi=rep(0,nn),mu=rep(0,nn))
  l <- 1
  
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      for(k.n in k)
      {
        
        flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"edges",n,
                              simtype,edgemu)
        edges <- read.csv(flnm)
        
        o <- length(edges$true_B)
        edges$edge <- 1:o
        edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,1,0))
        edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,1,0))
        edges <- transform(edges,zero_mean=ifelse(true_B == 0.0,1,0))
        edges <- transform(edges,fp=ifelse(rej==1 & nonzero_mean==0,1,0))
        edges <- transform(edges,fn=ifelse(rej==0 & nonzero_mean==1,1,0))
        
        fr.e$fpr_edges[l] <- sum(edges$fp) / sum(1 - edges$nonzero_mean)
        fr.e$fnr_edges[l] <- sum(edges$fn) / sum(edges$nonzero_mean)
        fr.e$pi[l] <- i.pi
        fr.e$mu[l] <- j.mu
        fr.e$n_microbes[l] <- k.n
        
        flnm2 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"nodes",n,
                               simtype,edgemu)
        nodes <- read.csv(flnm2)
        
        m <- length(nodes$TrueXi)
        nodes$node <- 1:m
        nodes <- transform(nodes, rej=ifelse(Xi.posterior>=0.5,1,0))
        nodes <- transform(nodes, TrueXi=ifelse(TrueXi=='true',TRUE,FALSE))
        nodes <- transform(nodes,fp=ifelse(rej==1 & TrueXi==FALSE,1,0))
        nodes <- transform(nodes,fn=ifelse(rej==0 & TrueXi==TRUE,1,0))
        
        fr.e$fpr_nodes[l] <- sum(nodes$fp) / sum(1 - nodes$TrueXi)
        fr.e$fnr_nodes[l] <- sum(nodes$fn) / sum(nodes$TrueXi)
        
        l <- l+1
      }
    }
  }
  
  ## Manipulate df
  df = gather(fr.e,"type","value",2:5)
  df = within(df, type <- factor(type))
  
  ## added something so that bars appear even with 0.0
  df$value[df$value == 0.0] = 0.005
  
  if(xaxis){
  xlabel = "Number of sampled nodes"
  }else{
  xlabel = ""
  }
  
  plt <- ggplot(data=df,aes(x=k,y=value,fill=type)) + 
    geom_bar(position="dodge", stat="identity") +
    ylab("")+xlab(xlabel)+
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(1.8)),
        axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"), 
        axis.text.y = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"),
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2)),
        legend.title = element_blank(),
        legend.text = element_text(size = rel(1.5))
        ) +
    scale_fill_manual(values=c("#82AFBC", "#9999CC", "#0E4B87", "#4C0099")) + 
    scale_x_continuous(breaks=k) +
    #guides(fill="none") +
    scale_y_continuous(position="right",breaks = c(0,0.5,1),limits=c(0,1)) + 
    facet_grid(pi ~ mu, 
               switch="y",
              labeller = labeller(
                mu = c(`0.8` = "\u03BC=0.8", `1.2` = "\u03BC=1.2", `1.4` = "\u03BC=1.4", `1.6` = "\u03BC=1.6"),
                pi = c(`0` = "\u03C0=0.0", `0.3` = "\u03C0=0.3", `0.5` = "\u03C0=0.5", `0.7` = "\u03C0=0.7", `0.8` = "\u03C0=0.8")
              ),
              as.table = FALSE)
  
  if(title){# && simtype != NULL){
     #tl_ar <- strsplit(simtype,"_")[[1]]
     #print(tl_ar)
     #if(tl_ar[2] == "phylo"){
    #   tl_ar[2] = "phylogenetic"
    # }
    # if(tl_ar[1] == "additive"){
     #  tl_ar[1] = "Additive"
     #}
     #else if(tl_ar[1] == "interaction")
     #{
    #   tl_ar[1] = "Interaction"
     #}
     #else
     #{
    #   tl_ar[1] = "Functional redundancy"
     #}
     #print(tl_ar)
     #plt <- plt + ggtitle(paste0(tl_ar,collapse=" ")) + theme(legend.position = "top")
    plt <- plt + ggtitle(paste0("n = ",n)) + theme(legend.position = "top")
  }else{
      plt <- plt + theme(legend.position = "none") 
  }
  
  return(plt)
}
```

### 6. Plot credible intervals for nodes
```{r}
plot.ci.nodes <- function(simnum,pi,mu,R,nu,k,path,n,lim,simtype=NULL,edgemu=NULL, ylab=T,xticks=T)
{
  nodes <- data.frame()
  nonc <- rep(F,4)

  flnm2 <- make.filename(path,simnum,pi,mu,R,nu,k,"psrf",n,simtype,edgemu)
  psrf <- read.csv(flnm2)[1,]
  if ((psrf$max_gamma[1] > 1.01 || psrf$max_xi[1] > 1.01))
  {
    nonc <- T
  }
  flnm <- make.filename(path,simnum,pi,mu,R,nu,k,"edges",n,simtype,edgemu)
  edges <- read.csv(flnm)
  
  nn <- length(edges$true_B)
  edges$edge <- 1:nn
  edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,TRUE,FALSE))
  edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,TRUE,FALSE))
  
  label = "True inf."
  
  flnm3 <- make.filename(path,simnum,pi,mu,R,nu,k,"nodes",n,simtype,edgemu)
  nodes <- read.csv(flnm3)
  
  ## Labelling the nodes:
  nn <- length(nodes$TrueXi) / (length(pi)*length(mu))
  nodes$microbe <- rep(1:nn,length(pi)*length(mu))
  nonc <- F
  
  n.len <- length(nodes$TrueXi)
  
  mat <- matrix(0,n.len,n.len)
  mat[lower.tri(mat, diag=T)] <- edges$mean
  mat <- t(mat)
  
  lower.mat <- matrix(0,n.len,n.len)
  lower.mat[lower.tri(lower.mat, diag=T)] <- edges$X0.025
  lower.mat <- t(lower.mat)
  
  upper.mat <- matrix(0,n.len,n.len)
  upper.mat[lower.tri(upper.mat, diag=T)] <- edges$X0.975
  upper.mat <- t(upper.mat)
  
  nonzero.mat <- matrix(0,n.len,n.len)
  nonzero.mat[lower.tri(nonzero.mat, diag=T)] <- edges$nonzero_mean
  diag(nonzero.mat) <- as.factor(nodes$TrueXi)
  nonzero.mat <- t(nonzero.mat)
  
  rej.mat <- matrix(0,n.len,n.len)
  rej.mat[lower.tri(rej.mat, diag=T)] <- edges$rej
  rej.mat <- t(rej.mat)
  
  #print("main effect coefficients")
  coefdf <- data.frame(lower=diag(lower.mat),coef=diag(mat),
                       upper=diag(upper.mat),nodepp=nodes$Xi.posterior,
                       true_inf=nodes$TrueXi,
                       node=1:length(diag(lower.mat)),
                       nonzero_mean=as.factor(diag(nonzero.mat)),
                       rej = as.factor(diag(rej.mat))
                       )
  
  lim_low <- floor(min(coefdf$lower)) - 0.25
  lim_high <- ceiling(max(coefdf$upper)) + 0.25
  lim <- c(lim_low,lim_high)
  
  if(ylab){
    ylabel2 = "PP"
    axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
  }else{
    ylabel2 = ""
    axisTextY = element_blank()
  }
  if(ylab){
    ylabel = expression(beta)
    axisTextY = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain")
  }else{
    ylabel = ""
    axisTextY = element_blank()
  }
  if(xticks){
    xlabel = "Microbe"
    axisLabsX = element_text()
  }
  else
  {
    xlabel = ""
    axisLabsX = element_blank()
  }
  
  plt1 <- coefdf %>% ggplot() + geom_errorbar(aes(x=factor(node),ymin=lower,
                                                                 ymax=upper,
                                                                 color=rej)) +
        xlab("") + ylab(ylabel)+ #ggtitle(paste0("\u03C0=",pi," \u03BC=",mu))+
        scale_color_manual(values=c("#82AFBC","#0E4B87")) + 
        theme(
          plot.title = element_text(hjust=0.5, size=rel(2)),
          axis.title.x = element_text(size=rel(2)),
          axis.title.y = element_text(size=rel(2), angle=90, vjust=0.5, hjust=0.5),
          #axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
          axis.text.x=element_blank(), 
          axis.ticks.x=element_blank(),
          axis.ticks.y = element_blank(),
          panel.background = element_rect(fill = NA, color = "black"),
          axis.line = element_line(colour = "grey"),
          strip.text = element_text(size = rel(1.5)),
          legend.position = "none",
          plot.margin = margin(b=-0.25, unit="cm")
        ) +
          #scale_x_continuous(limits=c(1,n)) + coord_flip() +
          #scale_y_continuous(limits=lim) +
          #coord_flip() + scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          #scale_x_discrete(labels=NULL,expand=expansion(add=4)) +
          geom_point(aes(x=factor(node),y=coef, color=rej),shape=18, size=2) +
          geom_hline(aes(yintercept=0),linetype="solid",color="#696969", size=1) +
          ##geom_hline(aes(yintercept=mu),linetype="dashed",color="blue") +
          facet_grid(.~nonzero_mean,scales="free_x",space="free_x", 
                     labeller = labeller(
                                  nonzero_mean = c(`1` = "non-inf.",
                                                   `2` = "true inf.")
          ))
  
  view_lim <- c(max(lim_low,-10),min(lim_high,10))
  
  plt1 <- plt1 + coord_cartesian(ylim = view_lim)
  
  plt2 <- ggplot(data=coefdf,aes(x=factor(node),y=nodepp,fill=rej)) + 
    geom_bar(stat="Identity") + xlab(xlabel) + ylab(ylabel2) + 
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(2)),
        axis.title.y = element_text(size=rel(2), angle=90, vjust=0.5, hjust=0.5),
        #axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        #axis.text.y = axisTextY,
        #axis.text.x = element_text(colour="grey", size=rel(1.8), hjust=.5, vjust=.5, face="plain"),
        axis.text.x = axisLabsX,
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2)),
        strip.background = element_blank(),
        strip.text.x = element_blank(),
        plot.margin = margin(t=-0.25, unit="cm")
        ) +
  scale_fill_manual(values=c("#82AFBC","#0E4B87")) + 
    guides(fill="none") +
    scale_y_continuous(breaks = c(0,0.5,1),limits=c(0,1.05)) + 
    facet_grid(.~nonzero_mean,scales="free_x",space="free_x", 
                     labeller = labeller(
                                  nonzero_mean = c(`1` = "", 
                                                   `2` = "")
          ))
  
  #if(nonc)
  #{
  #  plt1 <- plt1 + ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu, " - NOT CONV."))
  #  plt2 <- plt2 + ggtitle(paste0("\u03C0=",pi,", \u03BC=",mu, " - NOT CONV."))
  #}

  return(list(plt1,plt2))
}
```



### 6. Create ROC curves
```{r}
plot.ROC <- function(simnum,pi,mu,R,nu,k,path,n,simtype=NULL,edgemu=NULL, ylab=TRUE, leg=TRUE,title=TRUE)
{
  
  nn <- length(k) * length(pi) * length(mu) * length(seq(0.1,1,0.05))
  fr.e <- data.frame(k=rep(0,nn),fpr_nodes=rep(0,nn), tpr_nodes=rep(0,nn),
                      pi=rep(0,nn),mu=rep(0,nn),n_microbes=rep(0,nn),cut=rep(0,nn))
  
  plts <- list()
  l <- 1
  
  for(i.pi in pi)
  {
    for(j.mu in mu)
    {
      for(xi.cut in seq(0.1,1,0.05))
      {
        #flnm <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"edges",n,
        #                      simtype,edgemu)
        #edges <- read.csv(flnm)
        
        #o <- length(edges$true_B)
        #edges$edge <- 1:o
        #edges <- transform(edges,rej=ifelse(X0.025 > 0 | X0.975 < 0,1,0))
        #edges <- transform(edges,nonzero_mean=ifelse(true_B != 0.0,1,0))
        #edges <- transform(edges,zero_mean=ifelse(true_B == 0.0,1,0))
        #edges <- transform(edges,fp=ifelse(rej==1 & nonzero_mean==0,1,0))
        #edges <- transform(edges,fn=ifelse(rej==0 & nonzero_mean==1,1,0))
        
        #fr.e$fpr_edges[l] <- sum(edges$fp) / sum(1 - edges$nonzero_mean)
        #fr.e$fnr_edges[l] <- sum(edges$fn) / sum(edges$nonzero_mean)
        #fr.e$pi[l] <- i.pi
        #fr.e$mu[l] <- j.mu
        #fr.e$n_microbes[l] <- k.n
        
        flnm2 <- make.filename(path,simnum,i.pi,j.mu,R,nu,k.n,"nodes",n,
                               simtype,edgemu)
        nodes <- read.csv(flnm2)
        
        m <- length(nodes$TrueXi)
        nodes$node <- 1:m
        nodes <- transform(nodes, rej=ifelse(Xi.posterior>=xi.cut,1,0))
        nodes <- transform(nodes, TrueXi=ifelse(TrueXi=='true',TRUE,FALSE))
        nodes <- transform(nodes,fp=ifelse(rej==1 & TrueXi==FALSE,1,0))
        nodes <- transform(nodes,fn=ifelse(rej==0 & TrueXi==TRUE,1,0))
        nodes <- transform(nodes,tp=ifelse(rej==1 & TrueXi==TRUE,1,0))
        
        fr.e$fpr_nodes[l] <- sum(nodes$fp) / sum(1 - nodes$TrueXi)
        fr.e$tpr_nodes[l] <- sum(nodes$tp) / sum(nodes$TrueXi)
        fr.e$pi[l] <- i.pi
        fr.e$mu[l] <- j.mu
        fr.e$n_microbes[l] <- k.n
        fr.e$cut[l] <- xi.cut
        
        l <- l+1
      }
    }
  }
  
  y_label = ""
  
  if(ylab)
  {
    y_label = "true positive rate"
  }
  
  plt <- ggplot(data=fr.e[order(fr.e$fpr_nodes,fr.e$tpr_nodes),],aes(x=fpr_nodes,y=tpr_nodes,
                              group=interaction(pi,mu),
                              color=factor(pi), 
                              linetype=factor(mu))
                              ) + 
    geom_line() + 
    ylab(y_label) + xlab("false positive rate") +
    theme(
        plot.title = element_text(hjust=0.5, size=rel(2)),
        axis.title.x = element_text(size=rel(1.8)),
        axis.title.y = element_text(size=rel(1.9), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"), 
        axis.text.y = element_text(colour="grey", size=rel(1.7), angle=0, hjust=.5, vjust=.5, face="plain"),
        panel.background = element_rect(fill = NA, color = "black"),
        axis.line = element_line(colour = "grey"),
        strip.text = element_text(size = rel(2)),
        legend.title = element_blank(),
        legend.text = element_text(size = rel(1.5))
        ) 
  
  if(title){
    plt <- plt + ggtitle(paste0("n = ",n)) + theme(legend.position = "top")
  }else{
      plt <- plt + theme(legend.position = "none") 
  }
  
  print(fr.e)
  
  return(plt)
}
```

#### Main Text:

n = 100,500
k = 8,15,22
R = 5,7,9
pi = 0.0,0.3,0.8
mu = 0.8,1.6

- n=100,k=8, R=7
- n=100,k=15, R=7
- n=100,k=22, R=7
- n=500,k=8, R=7
- n=500,k=15, R=7
- n=500,k=22, R=7

Fixed parameters for all plots:
```{r}
path = "~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/simulation/current-wid/unrealistic-results/"
nu=10
simnum = 1
pi = c(0.3,0.8)
mu = c(0.8,1.6)
all_k = c(8,15,22)
all_n = c(100,500)
all_R = c(5,7,9)
```


```{r}
for(R in all_R)
{
  for(n in all_n)
  {
    for(k in all_k)
    {
      ### ROC
      ROC.plots <- list(rep(0,2))
      a <- 1
      for(nn in all_n)
      {
        #MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,ks,path,n,simtype=simtype,leg=(n==100),edgemu=edgemu,maxlim=ifelse(n==100,maxlim,100),ylab=(n==50))
        
        ROC.plots[[a]] = plot.ROC(simnum,pi,mu,R,nu,k,path,nn,leg=(nn==500),ylab=(nn==100))
        a <- a + 1
      }
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-roc-n100_500-k",k,"-R",R,".pdf")
      pdf(plotname,height=6, width=10)
      #title <- ggdraw() + draw_label(paste0("R=",R,", k=",k), fontface='bold')
        
      plt1 <- plot_grid(ROC.plots[[1]],ROC.plots[[2]],nrow=1,align='h',rel_widths = c(1,1))
      print(plt1)
      #print(plot_grid(title,plt1,ncol=1,align='v',rel_heights = c(0.05,1)))
      dev.off()
  
      ### Intervals
      plts = list(rep(0,4))
      l <- 1
      for(i.pi in pi)
      {
        for(j.mu in mu)
        {
          plt = plot.intervals(simnum,i.pi,j.mu,R,nu,k,path,n,c(-8,8))
          plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-intervals-n",n,"-k",k,"-R",R,"-pi",i.pi,"-mu",j.mu,".pdf")
          
          pdf(plotname,height=14, width=4)
          print(plt)
          dev.off()
          
          plt = plot.ci.nodes(simnum,i.pi,j.mu,R,nu,k,path,n,c(-4,4), ylab=(i.pi==0.3), xticks=(j.mu==0.8), simtype=NULL,edgemu=edgemu)
          
          pilab <- FALSE
          mulab <- FALSE
          
          pilab <- (j.mu == 1.6)
          mulab <- (i.pi == 0.8)
          
          pg1 <- plot_grid(plt[[1]], plt[[2]], ncol=1, align="v", rel_heights = c(1.2,1))
          if(pilab && mulab)
          {  
            pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
            mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
            plts[[l]] <- plot_grid(pilab,plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08)),ncol=1,rel_heights = c(0.08,1))
          }
          else if(pilab)
          {
            pilab <- ggdraw() + draw_label(bquote(pi*"="*.(i.pi)),size=28)
            plts[[l]] <- plot_grid(pilab,pg1,ncol=1,rel_heights = c(0.08,1))
          }
          else if(mulab)
          {
            mulab <- ggdraw() + draw_label(bquote(mu*"="*.(j.mu)),angle=90,size=28)
            plts[[l]] <- plot_grid(pg1,mulab,ncol=2,rel_widths=c(1,0.08))
          }
          else{
            plts[[l]] <- pg1
          }
          l <- l + 1
        }
      }
      
      # node credible intervals
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-ci-nodes-n",n,"-k",k,"-R",R,".pdf")
          
      pdf(plotname,height=10, width=12)
      
      #title <- ggdraw() + draw_label(paste0("n=",n," k=",k," R=",R), fontface='bold')
      
      #print(plot_grid(title, plot_grid(plts[[2]], plts[[4]], plts[[1]], plts[[3]], ncol=2,align="v"), ncol=1, align="v", rel_heights = c(0.05,1)))
      print(plot_grid(plts[[2]], plts[[4]], plts[[1]], plts[[3]], ncol=2,align="v"))
      dev.off()
      
      ### Grid for MAP for B
      plt = plot.heatmap(simnum,pi,mu,R,nu,k,path,n)
      
      plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-B-n",n,"-k",k,"-R",R,".pdf")
      
      pdf(plotname,height=6, width=7)
      print(plt)
      dev.off()
  
    }
    ### False Pos/Neg
    plt = plot.false.pos.neg(simnum,pi,mu,R,nu,all_k,path,n)
    plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-rates-n",n,"-R",R,".pdf")
    
    pdf(plotname)
    print(plt)
    dev.off()
    
  }
  ### MSE
  MSE.plots <- list(rep(0,2))
  a <- 1
  for(n in all_n)
  {
    #MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,ks,path,n,simtype=simtype,leg=(n==100),edgemu=edgemu,maxlim=ifelse(n==100,maxlim,100),ylab=(n==50))
    
    MSE.plots[[a]] = plot.MSE(simnum,pi,mu,R,nu,all_k,path,n,leg=(n==500),ylab=(n==100))
    a <- a + 1
  }
  plotname = paste0("~/Documents/masters/research/bayesian_network_regression/bayesian_network_regression_imp/results/plots/simulation/final/unrealistic/plot-mse-n100_500-R",R,".pdf")
  pdf(plotname,height=6, width=10)

  #title <- ggdraw() + draw_label(paste0("R=",R), fontface='bold')
    
  plt1 <- plot_grid(MSE.plots[[1]],MSE.plots[[2]],nrow=1,align='h',rel_widths = c(1,1.2))
  print(plt1)
  #print(plot_grid(title,plt1,ncol=1,align='v',rel_heights = c(0.05,1)))
  dev.off()
}
```


